---
title: "Retrieving tweets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{retrieving_tweets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library("quotefinder")
library("rtweet")
library("dplyr")

twitter_token <- readRDS(file = "twitter_token.rds")
```


There are three main ways to retrieve tweets using Twitter's API:

1. get tweets from a single user (or many users, asking one by one)
1. get tweets from a list of users
1. get tweets from the streaming APIs, e.g. by searching for a keyword or hashtag

By itself, the excellent `rtweet` package commonly used to interact with the Twitter APIs with R, does not provide convenience functions to cache and store tweets, leaving this to the user. 

The present `quotefinder` package provides such functions in order to facilitate collecting and pre-processing tweets in order to feed them to the QuoteFinder app. All retrieved tweets are stored in dated local sub-folders.

## Getting tweets by user 

The following command will download all available tweets for the given users and store them locally. If they have been previously downloaded, it will download only newer tweets. 

```{r getting_tweets, eval=FALSE}
qf_get_tweets_by_user(users = c("Europarl_EN", "EuroParlPress"),
                      twitter_token = twitter_token)

```


## Getting tweets from lists

When there is a need to collect regularly tweets from hundreds or thousands of users, this approach quickly becomes impractical, as it is easier to hit the limits allowed by Twitter APIs. 

An easy solution is to create a list of users, and then make a single request to get recent tweets for all accounts included in the list.^[It is easy to create new lists by using `rtweet`s `post_list()` function.] 


```{r}
qf_get_tweets_from_list(slug = "current-meps",
                        owner_user = "EDJQuoteFinder",
                        n = 3200,
                        include_rts = FALSE,
                        twitter_token = twitter_token)
```



